\documentclass[conference]{IEEEtran}

% Packages that Cody added start here
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,shadows,positioning,calc}
\usepackage{listings}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\lstset{basicstyle=\small\ttfamily,
columns=flexible,
breaklines=true,
upquote=true
}
\usepackage{hhline}
% Packages that Cody added end here

% Adding in extra packages and commands that help to write about SchemaAnalyst
\input{preamble/packages}
\input{preamble/commands}

\begin{document}

\title{\textit{SchemaAnalyst}: Search-based Test Data Generation for Relational Database Schemas}

\author{\IEEEauthorblockN{Phil McMinn and Chris Wright}
\IEEEauthorblockA{University of Sheffield}
\and
\IEEEauthorblockN{Cody Kinneer, Colton McCurdy, Michael Camara\\ and Gregory M. Kapfhammer}
\IEEEauthorblockA{Allegheny College}}
\maketitle

\begin{abstract}

Data stored in relational databases plays a vital role in many aspects of life.  When this data in incorrect, the
services that depend on that data may be compromised.  The database schema is the artefact responsible for maintaining
the integrity of data. Because of this critical function, properly testing the database schema is a task of great
importance.  \sa~is a tool to support testing this vital software component.  \sa~uses a search-based approach to
generate high-quality test data for database schemas. \sa~is extensible, includes a comprehensive evaluation framework
for evaluating the quality of test data, and includes documentation. This paper presents the release of \sa~to enhance
the ability of practitioners to test database schemas.

\end{abstract}

\input{sections/introduction}
\input{sections/background}
\input{sections/technique}
\input{sections/implementation}
\input{sections/relatedwork}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bib/bibtex}

\end{document}


