%!TEX root=../icsme2016_tool_paper.tex

\section{Conclusions and Future Work}\label{sec:conclusion}

% Review the contributions of the presented tool

Many data-centric services rely on the quality of the underlying data. Much of this data is managed by relational
databases, and the database schema protects the integrity of the data.  Testing the schema for correctness is vital to
ensuring data quality. \sa~is a tool that generates test data for a relational database schema, thereby increasing
confidence in the schema's correctness. Using a search-based technique, \sa~is able to provide high-quality test data
across multiple DBMSs. The presented tool also includes an evaluation framework that provides
\numprovidedschemas~case-study schemas and support for efficient mutation analysis. In addition to being used in
\numuniquepapers~published studies, the presented tool is now available from \sawebsite~\cite{tool}. With an open-source
license and a modular design, \sa~is an extensible tool for search-based test data generation and mutation testing,
enabling the work of both researchers and practitioners.

% Discuss several areas for future work and cast a vision for the future of this tool

In future work, we will evaluate how \sa~helps the people who design and test relational database schemas. We will
also integrate the tool with others that support software maintenance activities like regression
testing~\cite{Kapfhammer2008} and fault localization~\cite{Clark2011}. Next, we will extend the tool~so that it enables
the testing of recently developed NoSQL systems. Ultimately, the current version of \sa, our planned extensions, and the
features and studies contributed by the new researchers and industrialists using this tool will yield a comprehensive
approach to testing data-centric applications.
