\section{Implementation}
\textit{SchemaAnalyst} is implemented as a Java program.  Designed with extensibility in mind, the
\textit{SchemaAnalyst} tool is divided into 13 packages. The \texttt{sqlrepresentation} package
provides an intermediate Java representation of data structures in relational databases,
providing representations for database tables, columns, expressions, datatypes, integrity
constraints, and other relevant objects. A \texttt{sqlparser} package is provided that utilizes the
General SQL Parser~\cite{} to convert schemas expressed in the Structured Query Language (SQL) to the
Java intermediate representation. The \texttt{testgeneration} package provides a representation of test
suites and test cases, as well as test requirements and the nine provided coverage criteria. The
\texttt{data} package furnishes the three provided test data generators, as well as various generic
datatype representations for use in test data generation. The \texttt{dbms} package provides support
for the three currently supported DBMSs, and includes the classes that enable interaction with
installed DBMSs. The \texttt{sqlwriter} package provides support for creating SQL statements for use
with DBMSs, and is used with the \texttt{javawriter} package to encode the generated test data as a
JUnit test suite. The \texttt{mutation} package provides the mutation analysis functionality, 
including the 14 provided mutation operators, mutant equivalence and reduction features, and virtual
test suite executors.
\begin{enumerate}
\item design overview 
\item usage / demo
\item discussion of extensibility
\end{enumerate}
