\section{Introduction}

Much of modern life is driven by data.  Healthcare, science, and commerce rely on information that is
stored in relational databases.  When this data is incorrect, passengers can have their flights
delayed, or patients may receive the wrong medication. The relational database schema is the artifact
that is responsible for safeguarding the integrity of the database. The vital role of the database
schema makes testing the schema a task of vital importance.

\textit{SchemaAnalyst} is a tool for generating high-quality test data in support of database schema
testing. Using a search-based approach, \textit{SchemaAnalyst} discovers test data instances that
comprehensively exercise the database schema. \textit{SchemaAnalyst} includes an evaluation framework
with a collection of real-world case study schemas, as well as a mutation analysis feature
that enables verifying the quality of the generated test data. Additionally, \textit{SchemaAnalyst}
is extensible, well documented, and available on GitHub with an open-source license~\cite{tool}.

\textit{SchemaAnalyst} has been used extensively to support research studies involving search-based
software testing~\cite{kapfhammer2013search,mcminn2015effectiveness,kinneer2015automatically}, and
mutation testing~\cite{wright2013efficient,wright2014impact,wright2015mutation}.

In summary, the key contributions of this work are as follows:

Key Contributions:
\begin{itemize}
\item \textit{SchemaAnalyst}, an extensible tool for test data generation.
\item A comprehensive evaluation framework inc. schemas and mutation analysis tools.
\item Documenation explaining the features and usage of the tool.
\end{itemize}
